Summary Tables

### 2020-02-12 summary_tables_outcomes.Rmd
Use table of contents
Fix header

---
title: "Summary Tables"
output: html_document
---

@@

Click here: [change in yll](#change_yll_100k)

@@

## Change in YLL due to disease per 100,000 {#change_yll_disease_100k}

>>>>

---
title: "Summary Tables"
output:
  html_document:
    toc: true
    theme: united
---

@@

@@

### Change in YLL due to disease per 100,000 {#change_yll_disease_100k}
